---
title: "Extract microhabitat data"
output: html_document
date: "2025-10-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

0. start up
```{r pacakges_and_data}

rm(list=ls())

library(tidyverse)
library(sf)
library(raster)
library(terra)
library(exactextractr)
library(doParallel)
library(foreach)
library(starsExtra)
library(spatialEco)
library(rcrisp)
library(envirem)
library(spatstat.geom)
library(spatstat.random)
library(RANN)
library(MultiscaleDTM)

source("2_R/code/helper_functions.R")

projCRS <- 26913
pops <- c("SN1","SN2","SN3","SN4")
aggregation_factor = 1 # 1 = no aggregation

spatial.growth.df <- read_sf("2_R/outputData/Niwot demog/spatial/niwotGrowthDrone.shp") %>% 
  st_transform(.,projCRS)

pop_elevs <- data.frame(pop = pops,elev = NA)

# 1m 3DEP DEM
dem1m <- raster("2_R/inputData/Niwot/DEMs/NiwotRidge_1m.tif") 
dem1m_terra <- rast(dem1m)
# plot(dem1m)
# plot(dem1m_terra)
# dem1m_terra <- terra::project(dem1m_terra,paste0("EPSG:",projCRS) )
# dem1m <- raster(dem1m_terra)
```

# Read in plant markers to create transect polygons, then crop the polygons to exclude the area that likely contains most plants
```{r more_data}
set.seed(25)  # reproducible random points
plant.mask.buffer <- 0.2
min.bg.dist <- 0.1
n.bg.points <- 1000

bg.point.counts <- data.frame(pop = pops,
                              count = NA)

exclude_silene_area = TRUE

plot.list <- list()
for (pop in pops) {
  
  # Marker shapefile
  shp_path <- file.path("2_R/inputData/Niwot/markers/drone", paste0(pop, ".shp"))
  tmp <- read_sf(shp_path) %>% st_transform(projCRS)

  # Polygons from transect corner point markers
  tmp_polys <- tmp %>%
    filter(str_detect(NAME, "TR")) %>%
    mutate(transect = str_sub(NAME, 1, 3)) %>%
    group_by(transect) %>%
    summarise(geometry = st_combine(geometry), .groups = "drop") %>%
    st_convex_hull() %>%
    st_zm(drop = TRUE) 
  assign(paste0(pop, ".TRs"), tmp_polys, envir = .GlobalEnv)
  
  total.area <- sum(st_area(tmp_polys))
  
  # Single centroid for the pop area
  tmp_center <- tmp_polys %>%
    summarise(geometry = st_union(geometry)) %>%  # dissolve all TRs
    st_centroid()
  assign(paste0(pop, ".center"), tmp_center, envir = .GlobalEnv)

  # Elevation offset from 1 m DEM (bilinear, not rounded)
  pop.elev <- raster::extract(dem1m, sf::st_coordinates(tmp_center), method = "bilinear")
  pop_elevs$elev[pop_elevs$pop == pop] <- pop.elev

  # Filter for plant points (exclude TR, cm, spaces, tiePoint)
  tmp_plants <- tmp %>%
    filter(!str_detect(NAME, "TR"),
           !str_detect(NAME, "cm"),
           !str_detect(NAME, " "),
           !str_detect(NAME, "tiePoint")) %>%
    dplyr::select(-FID) %>%
    st_zm()
  
  if(exclude_silene_area==T){
  
    # buffer around all plant points; union to “swiss cheese” cutter
    tmp_plants_mask <- st_buffer(tmp_plants, plant.mask.buffer) %>% st_union()
    
    # Cut plant areas out of transect polygons
    bg_point_trs <- st_difference(tmp_polys, tmp_plants_mask) #tmp_polys #
    bg_point_trs_owin <- as.owin(bg_point_trs)
  
    pp <- rSSI(r = min.bg.dist, n = n.bg.points, win = bg_point_trs_owin, giveup = 5000)
    
      # Convert pp (spatstat point pattern) to sf dataframe
    tmp_bg_pts <- st_as_sf(as.data.frame(coords(pp)),
                           coords = c("x", "y"),
                           crs = st_crs(bg_point_trs)) %>%
      mutate(NAME = "background")
    
  } else {
    
    # Cut plant areas out of transect polygons
    bg_point_trs <- tmp_polys
    bg_point_trs_owin <- as.owin(bg_point_trs)
  
    pp <- rSSI(r = min.bg.dist, n = n.bg.points, win = bg_point_trs_owin, giveup = 5000)
    
    # Convert pp (spatstat point pattern) to sf dataframe
    tmp_bg_pts <- st_as_sf(as.data.frame(coords(pp)),
                           coords = c("x", "y"),
                           crs = st_crs(bg_point_trs)) %>%
      mutate(NAME = "background")
  }

  bg.point.counts$count[bg.point.counts$pop==pop] <- nrow(tmp_bg_pts)
  
  plot.list[[pop]] = ggplot()+
    geom_sf(data=bg_point_trs)+
    geom_sf(data=tmp_bg_pts,size=0.25)+
    ggtitle(pop)+
    theme_classic()
    
  # Combine plants + random
  tmp_allPoints <- rbind(tmp_plants, tmp_bg_pts) # %>%  mutate(point_type = ifelse(NAME=="random","background","plant"))
  assign(paste0(pop, ".plants"), tmp_allPoints, envir = .GlobalEnv)
  
  # Drone DEM (cm-scale), align CRS, add absolute elevation offset
  dem_path <- file.path("2_R/inputData/Niwot/DEMs/drone", paste0(pop, "_1cm.tif"))
  tmp_ras <- raster(dem_path)
  crs(tmp_ras) <- paste0("EPSG:", projCRS)
  tmp_ras <- tmp_ras + pop.elev

  if (aggregation_factor != 1) {
    tmp_ras <- aggregate(tmp_ras, fact = aggregation_factor)
  }

  assign(paste0(pop, ".dem.", aggregation_factor, "cm"), tmp_ras, envir = .GlobalEnv)
  
  # Clean up
  rm(shp_path, tmp, tmp_polys, tmp_center, tmp_plants, tmp_plants_mask,
     bg_point_trs, tmp_bg_pts, tmp_allPoints, tmp_ras, pop.elev)

  }

cowplot::plot_grid(plotlist = plot.list)

```

# Extract microhabitat data
## Slope and aspect first
```{r slope_and_aspect}

# Extract slope/aspect data using exactextractr for coverage-weighted extraction
radii_m <- c(0.05, 0.1, 0.2, 0.3, 0.4, 0.5)
for(pop in pops){
  
  print(pop)
  
  # Get the data for this population
  points <- get(paste0(pop, ".plants"))
  dem <- get(paste0(pop, ".dem.",aggregation_factor,"cm"))
  dem_terra <- rast(dem)
  
  # # Detrend raster to get average slope and aspect
  # dem_stars <- st_as_stars(dem_terra)
  # 
  # # starsExtra to detrend DEM
  # dem_detrended_stars <- starsExtra::detrend(dem_stars)
  # dem_detrended <- rast(dem_detrended_stars)[[1]]
  # dem_trend <-  rast(dem_detrended_stars)[[2]]
  # 
  # # Save detrended DEM and trend surface for future use
  # writeRaster(dem_detrended,
  #             file.path("2_R/inputData/Niwot/DEMs/drone", paste0(pop, "_1cm_detrended.tif")),
  #             overwrite = TRUE)
  # writeRaster(dem_trend,
  #             file.path("2_R/inputData/Niwot/DEMs/drone", paste0(pop, "_1cm_trend.tif")),
  #             overwrite = TRUE)

  dem_trend <- rast(paste0("2_R/inputData/Niwot/DEMs/drone/",pop,"_1cm_trend.tif"))
  
  # Calculate terrain using raster package for exactextractr compatibility
  micro_terrain_raster <- terra::terrain(dem_terra, v = c("slope","aspect"), unit = "degrees")
  trend_terrain_raster <- terra::terrain(dem_trend, v = c("slope","aspect"), unit = "degrees")

  # Eastness and northness from aspect
  micro_east <- sin(micro_terrain_raster[["aspect"]] * pi/180)
  micro_north <- cos(micro_terrain_raster[["aspect"]] * pi/180)
  trend_east <- sin(trend_terrain_raster[["aspect"]] * pi/180)
  trend_north <- cos(trend_terrain_raster[["aspect"]] * pi/180)

  # Extract point elevation (1cm buffer, coverage-weighted)
  buf_point <- st_buffer(points, 0.01)
  points$mc_elv_pt <- exact_extract(dem, buf_point, fun = "mean", progress = FALSE)

  # Loop through buffer widths for slope and aspect
  for(rad in radii_m){

    # Create buffer
    buf_big <- st_buffer(points, rad)

    # Extract slope from detailed (coverage-weighted mean)
    points[[paste0("mc_slp_", rad*100)]] <- exact_extract(
      micro_terrain_raster[["slope"]],
      buf_big,
      fun = w_mean,
      progress = FALSE
    )

    # Extract slope from trend (microvariation removed) raster
    points[[paste0("mc_slpT_", rad*100)]] <- exact_extract(
      trend_terrain_raster[["slope"]],
      buf_big,
      fun = w_mean,
      progress = FALSE
    )
    
    # Extract aspect (coverage-weighted circular mean)
    points[[paste0("mc_asp_", rad*100)]] <- exact_extract(
      micro_terrain_raster[["aspect"]],
      buf_big,
      fun = w_circ_mean_deg,
      progress = FALSE
    )
    
    points[[paste0("mc_aspT_", rad*100)]] <- exact_extract(
      trend_terrain_raster[["aspect"]],
      buf_big,
      fun = w_circ_mean_deg,
      progress = FALSE
    )

    # Extract eastness and northness
    points[[paste0("mc_est_", rad*100)]] <- exact_extract(
      micro_east,
      buf_big,
      fun = w_mean,
      progress = FALSE
    )

    points[[paste0("mc_nrth_", rad*100)]] <- exact_extract(
      micro_north,
      buf_big,
      fun = w_mean,
      progress = FALSE
    )

    points[[paste0("mc_estT_", rad*100)]] <- exact_extract(
      trend_east,
      buf_big,
      fun = w_mean,
      progress = FALSE
    )

    points[[paste0("mc_nrthT_", rad*100)]] <- exact_extract(
      trend_north,
      buf_big,
      fun = w_mean,
      progress = FALSE
    )
  }
  
  points <- points %>% 
    mutate(x = st_coordinates(geometry)[,"X"],
           y = st_coordinates(geometry)[,"Y"],
           local.x = round(x - min(x),2),
           local.y = round(y - min(y),2) ) %>% 
    relocate(c(x,local.x,y,local.y),.after = geometry) %>% 
    dplyr::select(-c(x,y))
  
  # Assign back to global environment
  assign(paste0(pop, ".plants"), points, envir = .GlobalEnv)
}
# write_csv(pop_elevs,"2_R/outputData/pop_elevs.csv")
```

# Extract TPI, TRI, curvature
```{r microtopo_metrics}

# Set up parallel processing (1 core/pop)
cl <- makeCluster(4)
registerDoParallel(cl)

# Export necessary objects to each cluster
clusterExport(cl, c("pops", "radii_m", "w_range", "w_circ_mean_deg","sky_exposure_niwot",
                    "SN1.plants", paste0("SN1.dem.",aggregation_factor,"cm"),
                    "SN2.plants", paste0("SN2.dem.",aggregation_factor,"cm"),
                    "SN3.plants", paste0("SN3.dem.",aggregation_factor,"cm"),
                    "SN4.plants", paste0("SN4.dem.",aggregation_factor,"cm")),
              envir = environment())

# Run parallel for loops
results <- foreach(pop = pops,
                   .packages = c("tidyverse", "sf", "raster", "terra",
                                "exactextractr", "starsExtra", "spatialEco","MultiscaleDTM")) %dopar% {

  # Get the data for this population
  points <- get(paste0(pop, ".plants"))
  # tiny point buffer for point extraction
  buf_point <- sf::st_buffer(points, 0.01)
  dem <- get(paste0(pop, ".dem.",aggregation_factor,"cm"))
  dem_terra <- rast(dem)

  # Create plant buffers for all radii_m and name them
  buffers <- lapply(radii_m, function(r) st_buffer(points, r))
  names(buffers) <- paste0(radii_m * 100, "cm")

  # ----- NA cells for plants/points near edge of DEM -----
  # % NA coverage inside the largest (1 m) buffer
  i_max <- which.max(radii_m)
  
  points$mc_napct <- exactextractr::exact_extract(
    dem_terra, buffers[[i_max]],
    function(v, cf) 100 * sum(is.na(v) * cf, na.rm = TRUE) / sum(cf, na.rm = TRUE)
  )
  
  points$edge_flag <- points$mc_napct > 5   # >5% NA
  
  # ----- TPI ----- 
  for (i in seq_along(radii_m)) {
    r_m <- radii_m[i]; r_cm <- r_m * 100
  
    # Compute TPI
    tpi_r <- spatialEco::tpi(dem_terra, scale = r_m, win = "circle")

    points[[paste0("mc_tpi_", r_cm)]] <-
    exactextractr::exact_extract(tpi_r, buf_point, fun = w_mean)
  
    }

  # ----- TRI -----
  for (i in seq_along(radii_m)) {

    r_m <- radii_m[i]; r_cm <- r_m * 100
    s.i <- radii_m[i]*100*2+1

    # Calculate TRI using terra::focal (faster than spatialEco::tri)
    # Using TRIrmsd (root mean squared deviation) instead of TRIriley
    # TRIrmsd is normalized by window size, making it comparable across scales
    # This is better for model selection across multiple radii (5cm to 50cm)

    # TRIrmsd formula (normalized by cell count):
    tmp.tri <- terra::focal(dem_terra,
                            w = s.i, # units = cells
                            fun = function(x) {
                             center_idx <- length(x) %/% 2 + 1
                             sqrt(sum((x - x[center_idx])^2, na.rm = TRUE) / sum(!is.na(x)))
                           })
    
    # Extract at point level (like TPI)
    points[[paste0("mc_tri_", r_cm)]] <-
      exactextractr::exact_extract(x = tmp.tri, y = buf_point, fun = w_mean)
  }
  
  ## ----- Curvature -----

  # Calculate plan and profile curvature using spatialEco
  # Plan curvature: perpendicular to slope - convergent (negative) vs divergent (positive)
  # Profile curvature: along slope - concave (negative) vs convex (positive)
  
  # Extract curvature at all radii
  for(i in seq_along(radii_m)) {
    r_m <- radii_m[i]
    r_cm <- r_m * 100

    # Create focal window (circular, same as TRI)
    window_size <- r_m * 100 * 2 + 1  # cells: 11x11 for 5cm, 61x61 for 30cm
    
    q.fit <- Qfit(r = dem_terra, w = c(window_size,window_size),metrics = c("profc","planc","maxc","meanc"))
    
    points[[paste0("mc_plcv_", r_cm)]] <-
      exact_extract(x=q.fit$planc, y=buf_point, fun=w_mean)

    points[[paste0("mc_prcv_", r_cm)]] <-
      exact_extract(x=q.fit$profc, y=buf_point, fun=w_mean)

    points[[paste0("mc_mncv_", r_cm)]] <-
      exact_extract(x=q.fit$meanc, y=buf_point, fun=w_mean)

    points[[paste0("mc_mxcv_", r_cm)]] <-
      exact_extract(x=q.fit$maxc, y=buf_point, fun=w_mean)
  }

  ## ---- HEAT LOAD INDEX ----

  # Extract Heat Load Index at multiple scales from pre-calculated HLI raster
  # Heat Load combines slope and aspect to estimate solar radiation potential
  # Uses spatialEco::hli

  # Calculate Heat Load Index from drone DEM (do once, extract later)
  hli <- spatialEco::hli(dem_terra)
  
  for(i in seq_along(radii_m)) {
    radius_cm <- radii_m[i] * 100

    # Extract Heat Load Index
    points[[paste0("mc_hl_", radius_cm)]] <-
      exact_extract(raster(hli), buffers[[i]], fun = w_mean, progress = FALSE)
  }
  
  return(points)

}

# Stop cluster
stopCluster(cl)

# Assign results back to global environment
for(i in 1:length(pops)){
  
  assign(paste0(pops[i], ".plants"), results[[i]], envir = .GlobalEnv)

  }

```

### Crop 1m 3DEP data 
```{r crop_1mDEM}

# # Get all population centroids
# all_centroids <- rbind(
#   SN1.center,
#   SN2.center,
#   SN3.center,
#   SN4.center
# )
# 
# # Create a convex hull around all centroids
# study_area_hull <- st_union(all_centroids) %>%
#   st_convex_hull()
# 
# # Buffer generously to avoid any edge effects
# # 100m buffer should be very safe (way more than the 1 pixel needed)
# study_area_buffered <- st_buffer(study_area_hull, 1000)
# ras_mask <- st_bbox(study_area_buffered)
# 
# # Crop the 1m DEM to this extent
# dem1m_terra_cropped <- crop(dem1m_terra, ras_mask)
# plot(dem1m_terra_cropped)
# 
# # Now use dem_cropped for all calculations
# dem1m_cropped <- raster(dem1m_terra_cropped)
# plot(dem1m_cropped)
# writeRaster(dem1m_cropped,filename = "2_R/inputData/Niwot/DEMs/croppedNiwotDEM.tif",overwrite=T)

dem1m_terra_cropped <- dem1m_terra <- rast("2_R/inputData/Niwot/DEMs/croppedNiwotDEM.tif")
dem1m_cropped <- raster(dem1m_terra)
```

### Microtopography from 1 m USGS 3DEP data
```{r micro_from_1m}

for (pop in pops) {

  # Per-pop geometry & points
  points <- get(paste0(pop, ".plants"))
  trs    <- get(paste0(pop, ".TRs")) %>% 
    sf::st_union() %>% 
    st_buffer(10) %>% 
    vect()

  # Now use dem__cropped for all calculations
  dem1m_popCrop <- terra::crop(x = dem1m_terra,y = trs)
  
  # Tiny buffer so exact_extract does coverage-weighting but acts like a point
  buf_pt <- sf::st_buffer(points, 0.001)

  # --- slope/aspect in degrees (Queen’s neighbors = 8) ---
  trn_deg_1m <- terra::terrain(dem1m_popCrop, v = c("slope","aspect"),
                               unit = "degrees", neighbors = 8)
  points$m1_elv_pt  <- exactextractr::exact_extract(dem1m_popCrop,  buf_pt, w_mean)
  points$m1_slp  <- exactextractr::exact_extract(raster::raster(trn_deg_1m[["slope"]]),  buf_pt, w_mean)
  points$m1_asp <- exactextractr::exact_extract(raster::raster(trn_deg_1m[["aspect"]]), buf_pt, w_circ_mean_deg)

  # --- TPI (3×3 Queen’s) ---
  tpi_1m <- spatialEco::tpi(dem1m_popCrop, scale = 3, win = "rectangle")
  points$m1_tpi <- exactextractr::exact_extract(raster::raster(tpi_1m), buf_pt, w_mean)

  # --- TRI (3×3, neighbors = 8) ---
  # Using TRIrmsd for consistency with drone TRI (normalized by cell count)
  tri_1m <- terra::terrain(dem1m_popCrop, v = "TRIrmsd", neighbors = 8)
  points$m1_tri <- exactextractr::exact_extract(raster::raster(tri_1m), buf_pt, w_mean)

  # --- Curvature (Z&T 3×3) ---
  cv_pl_1m  <- spatialEco::curvature(dem1m_popCrop, type = "planform")
  cv_pr_1m  <- spatialEco::curvature(dem1m_popCrop, type = "profile")
  cv_mag_1m <- sqrt(cv_pl_1m^2 + cv_pr_1m^2)

  points$m1_plcv  <- exactextractr::exact_extract(raster::raster(cv_pl_1m),  buf_pt, w_mean)
  points$m1_prcv  <- exactextractr::exact_extract(raster::raster(cv_pr_1m),  buf_pt, w_mean)
  points$m1_mgcv <- exactextractr::exact_extract(raster::raster(cv_mag_1m), buf_pt, w_mean)

  # --- Heat Load Index (McCune & Keon) ---
  hli_1m <- spatialEco::hli(dem1m_popCrop)
  points$m1_hl <- exactextractr::exact_extract(raster::raster(hli_1m), buf_pt, w_mean)

  # Assign back
  assign(paste0(pop, ".plants"), points, envir = .GlobalEnv)
}
```

# Extract mesotopography metrics from 1m DEM
# These are POPULATION-LEVEL metrics - all plants in a population get the same values
# This represents the traditional approach to habitat characterization
```{r mesotopo_metrics}

# Define mesotopography radii (m-scale)
meso_radii <- c(5, 10, 50)  # 5m, 25m, 50m radii

# Calculate terrain from 1m DEM (do once, use for all extractions)
terrain_1m <- raster::terrain(dem1m_cropped, opt = c("slope","aspect","TRI"), unit = "degrees")

# Heat Load Index (McCune & Keon 2002)
hli_1m <- spatialEco::hli(dem1m_terra_cropped)

# Curvature (plan and profile)
curv_plan_1m <- spatialEco::curvature(dem1m_terra_cropped, type = "planform")
curv_profile_1m <- spatialEco::curvature(dem1m_terra_cropped, type = "profile")
curv_tot_1m <- spatialEco::curvature(dem1m_terra_cropped, type = "total")
curv_mag_1m <- sqrt(curv_plan_1m^2 + curv_profile_1m^2)
curv_mean_1m     <- (curv_plan_1m + curv_profile_1m) / 2

# Extract mesotopography for each population
# Use population polygon buffered at different radii
for(pop in pops){

  # Get population polygon (outline of all transects)
  pop_polygon <- get(paste0(pop, ".TRs")) %>% st_union()

  # Create dataframe to store population-level metrics
  pop_meso_metrics <- data.frame(pop = pop)

  # Loop through mesotopo radii
  for(radius in meso_radii){

    # Buffer population polygon at this radius
    buffer <- st_buffer(pop_polygon, radius)

    # elevation
    pop_meso_metrics[[paste0("ms_elv_", radius)]] <-
      exact_extract(dem1m_cropped, buffer, fun = w_mean, progress = FALSE)

    # slope
    pop_meso_metrics[[paste0("ms_slp_", radius)]] <-
      exact_extract(terrain_1m[["slope"]], buffer, fun = w_mean, progress = FALSE)

    # aspect
    pop_meso_metrics[[paste0("ms_asp_", radius)]] <-
      exact_extract(terrain_1m[["aspect"]], buffer, fun = w_circ_mean_deg, progress = FALSE)

    # Heat Load Index
    pop_meso_metrics[[paste0("ms_hl_", radius)]] <-
      exact_extract(raster(hli_1m), buffer, fun = w_mean, progress = FALSE)

    # TRI (Terrain Ruggedness Index)
    pop_meso_metrics[[paste0("ms_tri_", radius)]] <-
      exact_extract(terrain_1m[["tri"]], buffer, fun = w_mean, progress = FALSE)

    # plan curvature (convergence/divergence)
    pop_meso_metrics[[paste0("ms_plcv_", radius)]] <-
      exact_extract(raster(curv_plan_1m), buffer, fun = w_mean, progress = FALSE)

    # profile curvature (concave/convex)
    pop_meso_metrics[[paste0("ms_prcv_", radius)]] <-
      exact_extract(raster(curv_profile_1m), buffer, fun = w_mean, progress = FALSE)
    
    # total curvature (concave/convex)
    pop_meso_metrics[[paste0("ms_tocv_", radius)]] <-
      exact_extract(raster(curv_tot_1m), buffer, fun = w_mean, progress = FALSE)
    
    # curvature magnitude
    pop_meso_metrics[[paste0("ms_macv_", radius)]] <-
      exact_extract(raster(curv_mag_1m), buffer, fun = w_mean, progress = FALSE)
    
    # curvature mean
    pop_meso_metrics[[paste0("ms_mncv_", radius)]] <-
      exact_extract(raster(curv_mean_1m), buffer, fun = w_mean, progress = FALSE)

   }

  # Join these population metrics to all plants in the population
  points <- get(paste0(pop, ".plants"))
  points <- points %>%
    mutate(pop = pop) %>%
    left_join(pop_meso_metrics, by = "pop")

  # Assign back to global environment
  assign(paste0(pop, ".plants"), points, envir = .GlobalEnv)
}

```

# Save final data
```{r save_data}

# Combine all populations
all_plants <- bind_rows(
  SN1.plants %>% mutate(pop = "SN1"),
  SN2.plants %>% mutate(pop = "SN2"),
  SN3.plants %>% mutate(pop = "SN3"),
  SN4.plants %>% mutate(pop = "SN4")
)

# Save
saveRDS(all_plants, "2_R/outputData/rawMicrotopoData/niwot_plants_micro_meso_topo.rds")
st_write(all_plants, "2_R/outputData/rawMicrotopoData/niwot_plants_micro_meso_topo.shp", delete_dsn = TRUE)
output_df <- as.data.frame(all_plants) %>% 
  dplyr::select(-geometry)
write_csv(output_df,"2_R/outputData/rawMicrotopoData/niwot_plants_micro_meso_topo.csv")

```


scratch - try shift
```{r}
# 
# 
# radius_m = 0.1
# offset_for_wind <- function(wind_dir, radius_m) {
#   rad <- wind_dir * pi / 180
#   dx <- radius_m * sin(rad)   # -x is west
#   dy <- radius_m * cos(rad)   # +y is north
#   c(dx = dx, dy = dy)
# }
# 
# sn1.pts <- SN1.plants %>% filter(NAME!="random") %>% st_buffer(0.01)
# sn1.10cm <- SN1.plants %>% filter(NAME!="random") %>% st_buffer(radius_m)
# 
# offsets <- offset_for_wind(300,0.1)
#   
# sn1.10cm.shifted <- sn1.10cm
# sn1.10cm.shifted$geometry <- sn1.10cm.shifted$geometry + offsets
# 
# 
# plot(sn1.10cm$geometry)
# plot(sn1.10cm.shifted$geometry,col="blue",add=T)
# plot(sn1.pts$geometry,add=T,col="red")
```

